---
title: "Class Survey Report"
author: "Hana Strickland, Sebastian Torres Retana, Rabab Ibrahim, Kelsie Johnson"
date: "5/11/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
source("a7.R")
```

# Summary

This informatics class requires students to learn programming. At the beginning of the class, students were asked to fill out a survey about their prior programming experience. Students rated their experience on a scale between 1 to 5.

>The survey:

> 1) I have never written code

> 2) I've experimented with simple programming

> 3) I have some experience with a programming language (e.g., took CSE142)

> 4) I have moderate experience with a programming language (e.g., took CSE143)

> 5) I have lots of experience with programming (e.g., beyond CSE 143)


We found the mean, median, maximum, and minimum for programming experience by both main operating system and informatics major interest.

We found that students who used the Windows operating system tended to have more experience than those using the Mac OS X operating system. The average rating for Windows users was `r mean_windows` while the average rating for Mac users was `r mean_mac`. However, there were students who used Windows that reported no programming experience and Mac OS X users who reported a lot of programming experience. Students who had experience with Linux had the most experience with programming. They had an average rating of `r mean_linux`. No one who's main operating system was Linux reported that they had below a moderate level of programming experience.

We found that students with an informatics interest tended to have more programming experience than those who were not sure, and students who were not sure tended to have more programming experience than those who were not interested in informatics. Students who were interested in informatics, unsure of informatics, and not interested in informatics had an average programming experience rating of `r mean_yes_info`, `r mean_unsure_info`, and `r mean_no_info`, respectively. However, all three categories included students who reported no programming experience and a lot of programming experience.

``` {r Part 3: First Visualizations, echo=FALSE, cache=FALSE, results=FALSE, warning=FALSE, response=FALSE, comment=FALSE, message=FALSE}
cli_experience_plot_2
vcs_experience_plot_2
md_experience_plot_2
r_experience_plot_2
web_experience_plot_2

```

